\documentclass{report}
\usepackage{titlesec}
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\newcommand{\RomanNumeralCaps}[1]
    {\MakeUppercase{\romannumeral #1}}
\usepackage{color}

\definecolor{mygreen}{rgb}{0.1,0.1,1.0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}
\lstset{ 
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}; should come as last argument
  basicstyle=\large\ttfamily,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  firstnumber=1,                % start line enumeration with line 1000
  frame=single,	                   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  language=C++,                 % the language of the code
  morekeywords={*,...},            % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mymauve},     % string literal style
  tabsize=2,	                   % sets default tabsize to 2 spaces \lstinputlisting; also try caption instead of title
}

\title{Lib UFG}
% \author{Rafael Castro }
\date{May 2019}

\begin{document}

\maketitle
 
 
\tableofcontents{}
    \chapter{Algebra \RomanNumeralCaps{1}}
    \section{Matrix Power}
    \subsection{Simple Matrix Power}
    (Original Problem: UVa 11486 - Finding Paths in Grid)
    \lstinputlisting{./solutions/SimpleMatrixPower.cpp}
    \subsection{Gauss Modular Equations}
    Given a tree (undirected unweighted graph), assign for each node in this a color $c_i$ ($0 \leq c_i \leq k - 1)$, such that for each node $i$, $c_i$ is the sum of colors adjacents to $i$ mod $k$.
    \bigskip
    Compute the number of differents possible colorings.
    \bigskip
    Solution $O(n^3)$.
    \bigskip
    (Original Problem: LightOJ 1279 - Graph Coloring).
    \lstinputlisting{./solutions/Algebra/GaussModular.cpp}
    \subsection{Chinese Remainder Theorem}
    Given (a, n, b, m), find a X that X = a mod n and X = b mod m, X is given mod LCM(n, m)
    \lstinputlisting{./solutions/Algebra/crt.cpp}
    
    \chapter{Data Structures \RomanNumeralCaps{2}}
    \section{Treap}
    \lstinputlisting{./solutions/DataStructures/Treap.cpp}
    \newpage
    \section{Segment Tree}
    \subsection{Simple Segment}
    \lstinputlisting{./solutions/DataStructures/segtree.cpp}
    \newpage
    \subsection{Segment with Lazy}
    \lstinputlisting{./solutions/DataStructures/segtreelazy.cpp}
    \newpage
    \subsection{Persistent Segment}
    Solution for Spoj Cunt on a Tree,
    Given a tree there are $Q$ queries where you need to find the $k$th minimum weigth in a path between $u$ and $v$, it also needs the lca and lca's father between $u$ and $v$.\newline
    Main idea is to build a segment tree for each node with a dfs starting from the root.
    \newline 
    Queries in $O(log(n))$
    \lstinputlisting{./solutions/DataStructures/persistent_segtree.cpp}
    \subsection{Unordered Set}
    Insert, delete and query relative position from a element in $O(logn)$.
    
    \bigskip
    
    Original Problem (Timus 1439 - Battle with You-Know-Who)
    
    \lstinputlisting{./solutions/DataStructures/UnorderedSet.cpp}
    
    \bigskip
    \subsection{Binary Lifting}
    Binary Search on a BIT in O(NlogN)
    
    \lstinputlisting{./solutions/DataStructures/binary_lifting.cpp}
    \section{Sparse Table}
    
    \subsection{Simple Sparse table}
    idempotent queries in $O(1)$, others $O(logn)$;
    \lstinputlisting{./solutions/DataStructures/sparsetable.cpp}
    \subsection{2D Sparse table}
    idempotent queries in $O(1)$;
    \lstinputlisting{./solutions/DataStructures/2Dsparsetable.cpp}
    \chapter{String \RomanNumeralCaps{4}}
    \section{String Hash}
    \lstinputlisting{./solutions/String/StringHash.cpp}
    
    \section{Suffix Array}
    Solution $O(nlogn)$ (Original 
    Problem UVa 12191 - File Recover).
    
    \bigskip
    
    \lstinputlisting{./solutions/String/SuffixArray.cpp}
    
    \chapter{Geometry \RomanNumeralCaps{8}}
    \section{Convex Hull}
        \subsection{Rotation Calipers}
        Diameter from a convex Polygon.
        
        Solution $O(n)$. Original Problem (NCPC 2013 - D).
        
        \lstinputlisting{./solutions/Geometry/MaxDistanceBetweenPoints.cpp}
        
        
    \section{Convex Hull Trick}
        \subsection{Convex Hull Trick 1}
        This solutions only works when the coeficients are all increasing / decreasing, and the queries decreasing / increasing. Improve $O(n^2)$ to $O(n)$. (Original Problem: Codeforces - Round 189 (Div. 1) C)
        \lstinputlisting{./solutions/ConvexHull1.cpp}
        \newpage
        \subsection{Convex Hull Trick 2}
        This solutions works under the same conditions for Convex Hull Trick 1, but it's used to solve problems in a 2D dinamic programming, like problem NKLEAVES from spoj. In resume we need to group $N$ leaves in $K$ groups, for each coordinate between 1 and $N$ there is a leaf with weight $w_i$, and the leaves can only be moved to the left, and the cost is $w_i * d$ where $d$ is the distance that leaf $i$ was moved. The problem asks for minimum cost to group the $N$ leaves in $K$ groups. Lets reverse the leaves weights, now the leafs can only be moved to the right.
        
        So, the recurrence is:
        
        \bigskip
        
        $dp_{i, j} = \min_{k \leq i} ( (\sum_{p=k}^{i} (i - p) * w_p) + dp_{k - 1, j - 1})$, clearly $O(n^2k)$
        
        \bigskip
        
        So we will keep our lines in such way, that we can solve this problem, see the code below. 
        
        This solutions only works when the coeficients are all increasing / decreasing, and the queries decreasing / increasing. Improve $O(n^2k)$ to $O(nk)$. (Original Problem: SPOJ - NKLEAVES)
        
        \lstinputlisting{./solutions/ConvexHullTrick2.cpp}
        \newpage
        \subsection{Convex Hull Trick 3 (Online Queries)}
        This solutions works without any assumption about the coeficients, in this case we will query is answered in $O(logn)$.
        
        Improve $O(n^2)$ to $O(nlogn)$. (Original Problem: Codeforces - Round 463 div1+div2 F. Escape Through Leaf)
        
        \lstinputlisting{./solutions/ConvexHullTrick3.cpp}
        \newpage
    \section{Line Sweep}
        \subsection{Points Inside Triangles}
        Given $n$ triangles with vertices {($x_i$, $y_i$), ($x_i + d$, $y_i$), ($x_i$, $y_i + d$)}, and $q$ points, compute for each triangle, the number of points that lie inside or in boundary of him. $O(nlogn)$. (Original Problem: CODECHEF - TRIANGULAR QUERIES)
        \lstinputlisting{./solutions/PointsInsideTriangles.cpp}
        \newpage
        \subsection{Ranking Problem}
        Given $n$ students that attended to $3$ contests, and all of them have different ranks, between $1$ and $n$ inclusive, for each contest. We say that one student $a$ is better that student $b$, if all ranks of student $a$ in each contest is lesser that student $b$. A student is said to be excellent if no other student is better than him. How many excelent students there exists ?
        
        This solutions runs in $O(nlogn)$. (Original Problem: SPOJ: NICEDAY)
        
        \lstinputlisting{./solutions/RankingProblem.cpp}
        \newpage
        \subsection{Balls Falls and Segments}
        Given $n$ segments (non horizontal and with no common points), and $m$ balls in a 2D plane, say for each ball the x point which he falls. (This solution was upload, the source code is just for only one ball, but the overall complexity is still $O(nlogn)$ if the number of balls is $O(n)$).
        
        This solutions runs in $O(nlogn)$. Original Problem (NCPC 2013 - H).
        
        \lstinputlisting{./solutions/WaterFalls.cpp}
        \newpage
        \subsection{Checking Points Inside Convex Polygon}
            \subsubsection{Offline}
            Given $n$ points in 2D plane, and a Convex Polygon, check for each of these $n$ points, if them are strict inside or not of polygon.
            
            This solutions runs in $O(nlogn)$ but i used Fracion Class to Take Care with double error precisions, so the overall solution in this case is $O(nlogn^2)$.
            
            \lstinputlisting{./solutions/PointsInsideConvexPolygon.cpp}
            \newpage
            \subsubsection{Online}
            Given one point and a Convex Polygon, with vertices in counter clockwise order, check if this point is inside or in boundary of him.
            
            This solutions runs in $O(logn)$.
            
            \lstinputlisting{./solutions/PointsInsideConvexPolygonOn.cpp}
        \newpage
        \subsection{Area of Rectangles Union}
        Given a set of N axis aligned rectangles, you need to find the area of their union. Each rectangle is represented by two points, one lower-left point and one upper-right point. The coordinates are all integers.
        
        This solutions runs in $O(nlogn)$. Original Problem (HackerEarth - Line Sweep Tutorial, Sample Exercicise)
        
        \lstinputlisting{./solutions/Geometry/RectangleUnion.cpp}
    \newpage
    \section{Minimum Perimeter Triangle}
    Given $n$ points in a 2D plane, return the minimum perimeter that can be formed taking three points, collinear points are allowed. $O(nlogn)$. (Original Problem - Google Code Jam WF 2009 - B)
    \lstinputlisting{./solutions/MinPerimeterTriangle.cpp}
    \chapter{Graph \RomanNumeralCaps{9}}
    \section{Flow}
        \subsection{MinCostMaxFlow}
            The problem is given a Graph with a source and sink vertices, each edge has a capacity $c_i$ and cost $l_i$ per unit of flow, compute the minimum cost to transport a max flow in this network. We will show some algorithm that solve this problem.
            \subsubsection{Cycle Canceling Algorithm}
            This algorithm takes a residual graph and max flow $f$ (eg. ford fulkerson algorithm for maximum flow), and compute the minimum cost to transport flow $f$ in this graph. It update the residual graph until graph a negative cycle, regard the edge costs, in the Graph. This implementation dont works with multiedges, this means that if edge $u->v$ exists then $v->u$ dont exists.
            
            \bigskip
            
            $O(nm^2CU)$, where $C$ is the maximum cost from a edge and $U$ maximum Capacity from a edge. (Original Problem - HackerEarth Minimum Cost Max Flow sample problem)
    
            \lstinputlisting{./solutions/Graph/CycleCancelingAlgorithm.cpp}
            \subsubsection{Sucessive Shortest Paths + SPFA ?}
            
            (Original Problem - UVa 11301 Great Wall of China $|V|$ = $10^4$ $|E|$ = $4.10^4$).
            
            \lstinputlisting{./solutions/Graph/SucessiveShortestPath.cpp}
    \section{2SAT}
    Given a formula like $\phi$ = $(a \lor b) \land (c \lor d) \land (e \lor f)...$, check if is possible assign values to the variables such that $\phi$ is evaluated to true.
    
    \bigskip
    
    Solution runs in $O(N + E)$, where $O(N)$ is the number of variables, and $O(E)$ is the number of clausules $(x_i \lor y_i)$. Original Problem(UVa 11930 - Rectangles)
    
    \lstinputlisting{./solutions/Graph/2SAT_tarjan.cpp}
    \section{Heavy Light Decomposition}
        \subsection{Can you answer these queries VII}
        Given are a tree with $n$ vertices, each vertice has a weight $x_i$, and two type of operations. Operation 1 asks for the maximum contiguous sum between two vertices $a$ and $b$. Operation 2 update the values of vertices between $a$ and $b$ to $c$. We have to process $Q$ operations.
        
        The problem can be solved with HLD in $O(Q(log(n))^2)$. Original Problem (SPOJ - GSS7).
        
        \lstinputlisting{./solutions/Graph/HLD.cpp}
        
        \subsection{Can you answer these queries VI}
        Given a tree with $n$ vertices, each vertice has a color (0 or 1), and two type of operations. Operation 0 asks for how many vertices are connected to a vertice $u$, when one vertice $v$ is connected to $u$ only if the path between $u$ and $v$ just contain vertices with same color of $u$ inclusive. Operation 1 is to change the color of vertice $u$ (0 to 1 and 1 to 0).
        
        The problem can be solved wih HLD in $O(Q(log(n))^2)$. Original Problem (SPOJ - Can You Answer These Queries VI).
        
        
        \lstinputlisting{./solutions/Graph/CanYouAnswerTheseQueriesVI.cpp}
    \chapter{Dynamic Programming }
    \section{Sum Over Subsets DP - SOS}
    \lstinputlisting{./solutions/DynamicProgramming/sos_dp.cpp}
    \chapter{Paradigms \RomanNumeralCaps{10}}
    \section{Binary Search}
    \subsection{Parallel Binary Search}
    (Original Problem: Atcoder Grand Contest 2 D)
     \lstinputlisting{./solutions/Algebra/agc002_d.cpp}
\end{document}